---
title: "Homework 5"
author: Tu  Nguyen
output: github_document
---

This is my solution to HW5.

```{r setup, include = FALSE}
library(tidyverse)
library(dplyr)
library(stringr)


knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 2

Load the data from a longitudinal study that included a control arm and an experimental arm, the file names include the subject ID and arm. 

```{r}
longitudinal_path = "./data"
longitudinal_files = list.files(longitudinal_path)

longitudinal_data = 
  longitudinal_files %>% 
  purrr::map(~ read_csv(file.path(longitudinal_path, .))) %>% 
  reduce(rbind)

longitudinal_df = 
  longitudinal_data %>% 
  mutate(subject_id = as.numeric(regmatches(longitudinal_files, regexpr( "\\d+", longitudinal_files))),
         arm = substr(longitudinal_files, start = 1, stop = 3)
  ) %>% 
  relocate(arm, subject_id, everything()) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week", 
    names_prefix = "week_",
    values_to = "observation_values"
  )
```

The following code chunk shows the spaghetti plot displaying the observations on each subject over time. 
Over the course of 8 weeks, there were not a lot of changes in observation values in the control arm participants. However, there seemed to be an increase of observation values after week 4 in overall observation values in the experimental arm participants. 

```{r}
longitudinal_df %>% 
  ggplot(aes(x = week, y = observation_values, group = subject_id, color = arm)) + 
  geom_path()
```




